Probability

### 2016-04-25 prob.tex
clean up first section

\documentclass{article}
\usepackage{fullpage}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsmath}

\theoremstyle{remark}
\newtheorem{example}{Example}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}

@@

A \emph{probability
  space}~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
collects necessary conditions for reasoning coherently about
collections of uncertain events. It consists of a \emph{sample space}
$\Omega$, a space of \emph{events}~$\events$, and a \emph{probability
  measure}~$\pmeas$. In this paper, we will only consider
\emph{finite} sets of events: we therefore define a sample space
$\Omega$ as an arbitrary non-empty finite set and the space of events
$\events$ as $2^\Omega$, the powerset of $\Omega$. Given the set of
events $\events$, the \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_i$,  of pairwise disjoint events, 
  $\pmeas(\bigcup E_i) = \sum \pmeas(E_i)$.
\end{itemize}

\begin{example}[Two-coin probability space]
  Consider an experiment that tosses two coins. We have four possible
  outcomes that constitute the sample space
  $\Omega = \{ HH, HT, TH, TT \}$. The event that the first coin is
  ``heads'' is $\{ HH, HT \}$; the event that the two coins land on
  opposite sides is $\{ HT, TH \}$; the event that at least one coin
  is tails is $\{ HT, TH, TT\}$. Depending on the assumptions
  regarding the coins, we can define several probability
  measures. Here is a possible one:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& 0 \\
\pmeas(\{ HH \}) &=& 1/3 \\
\pmeas(\{ HT \}) &=& 0 \\
\pmeas(\{ TH \}) &=& 2/3 \\
\pmeas(\{ TT \}) &=& 0 \\
\pmeas(\{  HH, HT \}) &=& 1/3 \\
\pmeas(\{  HH, TH \}) &=& 1 \\
\pmeas(\{  HH , TT \}) &=& 1/3 
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& 2/3 \\
\pmeas(\{  HT , TT \}) &=& 0 \\
\pmeas(\{  TH , TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH \}) &=& 1 \\
\pmeas(\{  HH, HT, TT \}) &=& 1/3 \\
\pmeas(\{  HH, TH, TT \}) &=& 1 \\
\pmeas(\{  HT, TH, TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH, TT \}) &=& 1
\end{array}
\end{array}\]
The assignment satisfies the two constraints for probability measures:
the probability of the entire sample space is 1, and the probability
of every collection of disjoint events (e.g.,
$\{ HT \} \cup \{ TH \}$) is the sum of the individual probabilities.
\end{example}

In a strict computational or experimental setting, one may question
the reliance of the definition of probability space on the uncountable
and uncomputable real interval $[0,1]$. This interval includes numbers
like $0.h_1h_2h_3\ldots$ where $h_i$ is 1 or 0 depending on whether
Turing machine $M_i$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\frac{\pi}{4}$
which can be computed but with increasingly large resources as the
precision increases. Therefore it is more appropriate in such
situations to consider probability measures mapping events to a finite
set of elements computable with a fixed set of
resources~\cite{Artstein1972,PuriRalescu1983}. The
simplest such set, and the one we will consider exclusively in this
paper, is the set
$\mathscr{L}_{2}=\left\{
  \textrm{impossible},\textrm{possible}\right\}$
together with the operation $\vee$ where
$x \vee y=\textrm{impossible}$ if and only if
$x=y=\textrm{impossible}$. In relation to the first definition, one
can interpret impossible as the closed interval $[0,0]$, possible as the
open interval $(0,1]$, and $\vee$ as the addition of intervals. The
definition of a probability measure in this case is modifed as being a
function $\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = \textrm{possible}$, and 
\item for a collection $E_i$,  of pairwise disjoint events, $\pmeas(\bigcup E_i) = \bigvee \pmeas(E_i)$.
\end{itemize}

\begin{example}[Two-coin probability space with finite set-valued
  probability measure.] Under the new set-valued requirement, the
  probability measure in the first example becomes:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& \textrm{impossible} \\
\pmeas(\{ HH \}) &=& \textrm{possible} \\
\pmeas(\{ HT \}) &=& \textrm{impossible} \\
\pmeas(\{ TH \}) &=& \textrm{possible} \\
\pmeas(\{ TT \}) &=& \textrm{impossible} \\
\pmeas(\{  HH, HT \}) &=& \textrm{possible} \\
\pmeas(\{  HH, TH \}) &=& \textrm{possible} \\
\pmeas(\{  HH , TT \}) &=& \textrm{possible} \\
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& \textrm{possible} \\
\pmeas(\{  HT , TT \}) &=& \textrm{impossible} \\
\pmeas(\{  TH , TT \}) &=& \textrm{possible} \\
\pmeas(\{  HH, HT, TH \}) &=& \textrm{possible} \\
\pmeas(\{  HH, HT, TT \}) &=& \textrm{possible} \\
\pmeas(\{  HH, TH, TT \}) &=& \textrm{possible} \\
\pmeas(\{  HT, TH, TT \}) &=& \textrm{possible} \\
\pmeas(\{  HH, HT, TH, TT \}) &=& \textrm{possible} 
\end{array}
\end{array}\]
\end{example}

@@

The mathematical framework above assumes that one has complete
knowledge of the events and their relationships. But even in many
classical situations, the structure of the event space is only
partially known and the precise dependence of two events on each other
cannot be determined with certainty. In the quantum case, this partial
knowledge is compounded by the fact that not all quantum events can be
observed simultaneously.  Indeed, in the quantum world, there are
non-commuting events which cannot even happen simultaneously. To
accommodate these more complex situations, we abandon the
sample space~$\Omega$ and define and reason directly about
events. A quantum probability space consist of just two
components: a set of events $\qevents$ and a probability measure
$\mu : \qevents \rightarrow [0,1]$. We give an example before giving
the formal definition.

Consider the one-qubit Hilbert space with computational basis
$\ket{0}$ and $\ket{1}$ and states:
\[
\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}, \qquad\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}\,.
\]
The set of events associated with this Hilbert space consists of all
projections including the empty projection $\mathbb{0}$ and the unit
projection $\mathbb{1} = \proj{0}+\proj{1}$:
\[ 
\{ \mathbb{0}, \proj{0}, \proj{1}, \proj{\ps}, \proj{\ms}, \ldots, \mathbb{1}\}
\]
Each event is interpreted as a possible post-measurement state of
a quantum system as follows: given some arbitrary current quantum state
$\ket{\psi}$ to be measured, the event $\proj{0}$ states that the
post-measurement state will be $\ket{0}$; the event $\proj{1}$ states
that the post-measurement state will be $\ket{1}$; the event
$\proj{\ps}$ states that the post-measurement state will be
$\ket{\ps}$; the event $\proj{\ms}$ states that the post-measurement
state will be $\ket{\ms}$; the event $\mathbb{1}$ states that the
post-measurement state will be a linear combination of $\ket{0}$ and
$\ket{1}$; and the event $\mathbb{0}$ states that the post-measurement
state will be the empty state.

In classical probability space, two particular coins can define a
probability measure on every event. Similarly, a quantum system can
define a quantum probability measure on its event. The difference
is that only orthogonal events can test together. For example, asking
whether event~$\mathbb{1}$ occurs is the same as asking whether
event~$\proj{0}$ or event~$\proj{1}$ occurs simultaniously. However,
we can never ask whether event~$\proj{0}$ or event~$\proj{-}$
occurs simultaniously. Similarly to the classical case, a \emph{quantum
probability space}~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}
can be summarized into the following two rules\footnote{Recently, people extend the domain of $\mu$ to all operators~$\mathcal{A}$
on $\Hilb$ and consider $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.
When an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$
is the expectation value of $A$. We does not take this approach because
we want to focus only on probability. }: 
\begin{itemize}
\item $\mu(\mathbb{1})=1$, and 
\item for a collection of pairwise orthogonal $E_{i}$, we have $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$. 
\end{itemize}
\begin{example}{[}One-qubit Hilbert space{]} Consider an experiment
that with a qubit. The events are discribed previously. Depending on
the systems, we can define different quantum probability measures.
Here is a possible one: 
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\mu_{0}\left(\mathbb{0}\right) & = & 0\\
\mu_{0}\left(\proj{0}\right) & = & 1\\
\mu_{0}\left(\proj{1}\right) & = & 0\\
 & \vdots
\end{array} & \begin{array}{rcl}
\mu_{0}\left(\mathbb{1}\right) & = & 1\\
\mu_{0}\left(\proj{\ps}\right) & = & 1/2\\
\mu_{0}\left(\proj{\ms}\right) & = & 1/2\\
 & \vdots
\end{array}\end{array}
\]
The assignment satisfies the two constraints for quantum probability
measures: the probability of $\mathbb{1}$ is 1, and the probability
of every summation of orthogonal events (e.g., $\proj{0}+\proj{1}$)
is the sum of the individual probabilities. \end{example}

@@

Although it seems that we need an infinite long table to specify the
quantum probability measure~$\mu_{0}$, our $\mu_{0}$ is actually
given by a simple formula~$\melement{0}{E}$. In general, Born discovered
each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
\begin{equation}
\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
The Born rule satisfies the following properties:
\begin{itemize}
\item It can be extend to mixed states. Given a mixed state represented
by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
the Born rule can be extended to $\rho$ by 
\begin{eqnarray}
\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}
Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
is a classical probability space. Therefore, when we discretize the
Hilbert space later, we may need to discretize this probability space
as well.\yutsung{Check!!!}
\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\yutsung{...I think I need to check these properties identify an
unique Born rule in CQT or something...}

@@

\yutsung{There are three ways to charactize a quantum probability: 
\begin{enumerate}
\item The above two conditions as Gleason did. 
\item As a linear functional on a {*} algebra. 
\item As induced by a state vector by the Born rule (\ref{eq:Born}). 
\end{enumerate}
According to equation (37) in section 4 Quantum Probability in \cite{Maassen2010},
the equalivance between 1. and 2. only hold for $d\ge3$ because of
Gleason' theorem. Therefore, it seems hard to get insight for how
to handle Gleason's theorem by {*}-algebra formulism...

The equalivance between 2. and 3. can be found in Proposition 4.1.1
in \cite{Swart2013}. Here, the Born rule~$\mu_{\psi}(E)$ is replaced
by a faithful pseudotrace $\tau$ and $\mu_{\psi}(E)=\tau\left(\proj{\psi}E\right)$.
The faithful pseudotrace is defined in section 5.2 Decomposition of
algebra with a list of conditions. The problem is:
\begin{itemize}
\item Lemma 5.2.1 proved there exists a faith pseudotrace, but said nothing
about uniqueness. Therefore, these conditions may not uniquely determine
the Born rule?
\item We don't formulate thing in algrebra... So although we may have an
analog or something, we cannot quite sure our conditions will be exactly
the same as theirs. 
\end{itemize}
If we admit the above, then the condition (a) to (c) and $\tau\left(AB\right)=\tau\left(BA\right)$
implies 
\begin{itemize}
\item Our map $\tilde{\mu}:\Hilb\rightarrow\qevents\rightarrow[0,1]$ should
satisfy $\tilde{\mu}_{\psi}$ is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
\end{itemize}
The condition (a) and (d) implies
\begin{itemize}
\item Our map $\tilde{\mu}$ satisfy $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
is impossible for $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $. 
\end{itemize}
$\tau\left(AB\right)=\tau\left(BA\right)$ also implies
\begin{itemize}
\item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
Besides, the condition (a) also gives the probability of mixed states
form pure states... OK... it seems that I know what I am going to
type for DQT, but I think I need to sort them out before type them...}

@@

>>>>

\documentclass{article}
\usepackage{fullpage}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsmath}
\usepackage{wesa}
\usepackage[T1]{fontenc}

\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}

@@

A \emph{probability
  space}~\cite{inun.425605319950101,GrahamKnuthPatashnik1994,rohatgi2011introduction}
specifies the necessary conditions for reasoning coherently about
collections of uncertain events. It consists of a \emph{sample space}
$\Omega$, a space of \emph{events}~$\events$, and a \emph{probability
  measure}~$\pmeas$. In this paper, we will only consider
\emph{finite} sets of events: we therefore define a sample space
$\Omega$ as an arbitrary non-empty finite set and the space of events
$\events$ as $2^\Omega$, the powerset of $\Omega$. Given the set of
events $\events$, a \emph{probability measure} is a function
$\pmeas : \events \rightarrow [0,1]$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = 1$, and 
\item for a collection $E_i$,  of pairwise disjoint events, 
  $\pmeas(\bigcup E_i) = \sum \pmeas(E_i)$.
\end{itemize}

\begin{example}[Two-coin probability space]
  Consider an experiment that tosses two coins. We have four possible
  outcomes that constitute the sample space
  $\Omega = \{ HH, HT, TH, TT \}$. There are 16 total events including
  for example the event $\{ HH, HT \}$ that the first coin is
  ``heads,'' the event $\{ HT, TH \}$ that the two coins land on
  opposite sides, and the event $\{ HT, TH, TT\}$ that at least one
  coin is tails. Here is a possible probability measure for these
  events:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& 0 \\
\pmeas(\{ HH \}) &=& 1/3 \\
\pmeas(\{ HT \}) &=& 0 \\
\pmeas(\{ TH \}) &=& 2/3 \\
\pmeas(\{ TT \}) &=& 0 \\
\pmeas(\{  HH, HT \}) &=& 1/3 \\
\pmeas(\{  HH, TH \}) &=& 1 \\
\pmeas(\{  HH , TT \}) &=& 1/3 
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& 2/3 \\
\pmeas(\{  HT , TT \}) &=& 0 \\
\pmeas(\{  TH , TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH \}) &=& 1 \\
\pmeas(\{  HH, HT, TT \}) &=& 1/3 \\
\pmeas(\{  HH, TH, TT \}) &=& 1 \\
\pmeas(\{  HT, TH, TT \}) &=& 2/3 \\
\pmeas(\{  HH, HT, TH, TT \}) &=& 1
\end{array}
\end{array}\]
The assignment satisfies the two constraints for probability measures:
the probability of the entire sample space is 1, and the probability
of every collection of disjoint events (e.g.,
$\{ HT, TH \} = \{ HT \} \cup \{ TH \}$) is the sum of the individual
probabilities. The probability of collections of non-disjoint events
(e.g., $\{ HT, TH, TT \} = \{ HT, TH \} \cup \{ TH , TT \}$) may add
to something different than the probabilities of the individual
events. It is useful to think that this probability measure is
completely induced by the two coins and their characteristics in the
sense that each pair of coins induces a measure, and each measure must
correspond to some pair of coins.
\end{example}

In a strict computational or experimental setting, one may question
the reliance of the definition of probability space on the uncountable
and uncomputable real interval $[0,1]$. This interval includes numbers
like $0.h_1h_2h_3\ldots$ where $h_i$ is 1 or 0 depending on whether
Turing machine $M_i$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\frac{\pi}{4}$
which can only be computed with increasingly large resources as the
precision increases. Therefore, in a resource-aware setting, it is
more appropriate to consider probability measures that map events to a
finite set of elements computable with a fixed set of
resources~\cite{Artstein1972,PuriRalescu1983}. The simplest such set,
and the one we will consider exclusively in this paper, is the set
$\mathscr{L}_{2}=\left\{ \imposs, \poss\right\}$ together with the
operation $\vee$ where $x \vee y=\imposs$ if and only if
$x=y=\imposs$. In relation to the first definition, one can interpret
\imposs\ as the closed interval $[0,0]$, \poss\ as the open interval
$(0,1]$, and $\vee$ as the addition of intervals. The definition of a
probability measure in this case is modified as being a function
$\pmeas : \events \rightarrow \mathscr{L}_{2}$ such that:
\begin{itemize}
\item $\pmeas(\Omega) = \poss$, and
\item for a collection $E_i$,  of pairwise disjoint events, $\pmeas(\bigcup E_i) = \bigvee \pmeas(E_i)$.
\end{itemize}

\begin{example}[Two-coin probability space with finite set-valued
  probability measure] Under the new set-valued requirement, the
  probability measure in the first example becomes:
\[\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) &=& \imposs \\
\pmeas(\{ HH \}) &=& \poss \\
\pmeas(\{ HT \}) &=& \imposs \\
\pmeas(\{ TH \}) &=& \poss \\
\pmeas(\{ TT \}) &=& \imposs \\
\pmeas(\{  HH, HT \}) &=& \poss \\
\pmeas(\{  HH, TH \}) &=& \poss \\
\pmeas(\{  HH , TT \}) &=& \poss \\
\end{array} & \begin{array}{rcl}
\pmeas(\{  HT, TH \}) &=& \poss \\
\pmeas(\{  HT , TT \}) &=& \imposs \\
\pmeas(\{  TH , TT \}) &=& \poss \\
\pmeas(\{  HH, HT, TH \}) &=& \poss \\
\pmeas(\{  HH, HT, TT \}) &=& \poss \\
\pmeas(\{  HH, TH, TT \}) &=& \poss \\
\pmeas(\{  HT, TH, TT \}) &=& \poss \\
\pmeas(\{  HH, HT, TH, TT \}) &=& \poss 
\end{array}
\end{array}\]
\end{example}

@@

The mathematical framework above assumes that one has complete
knowledge of the events and their relationships. However, in many
practical situations, the structure of the event space is only
partially known and the precise dependence of two events on each other
cannot, a priori, be determined with certainty. In the quantum case,
this partial knowledge is compounded by the fact that there exist
non-commuting events which cannot happen simultaneously. To
accommodate these more complex situations, we abandon the sample
space~$\Omega$ and reason directly about events. A quantum probability
space therefore consist of just two components: a set of events
$\qevents$ and a probability measure
$\mu : \qevents \rightarrow [0,1]$. We give an example before giving
the formal definition.

\begin{example}[One-qubit quantum probability space] 
  Consider a one-qubit Hilbert space with states
  $\alpha \ket{0} + \beta \ket{1}$ such that
  $|\alpha|^2 + |\beta|^2 = 1$. The set of events associated with this
  Hilbert space consists of the empty projection~$\mathbb{0}$ together 
  with projection operators $\proj{\psi}$ for each state $\ket{\psi}$.
  Each event is interpreted as a possible post-measurement state of a
  quantum system in current state $\ket{\phi}$. For example, the event
  $\proj{0}$ indicates that the post-measurement state will
  be~$\ket{0}$; the event $\proj{1}$ indicates that the
  post-measurement state will be~$\ket{1}$; the event $\proj{\ps}$
  where $\ket{\ps} = \frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$ indicates
  that the post-measurement state will be $\ket{\ps}$; the event
  $\mathbb{1} = \proj{0}+\proj{1}$ indicates that the post-measurement
  state will be a linear combination of $\ket{0}$ and $\ket{1}$; and
  the event $\mathbb{0}$ states that the post-measurement state will
  be the empty state. As in the classical case, a probability measure
  maps events to $[0,1]$: here is a partial specification of a
  possible measure:
\[\begin{array}{rcl}
\mu\left(\mathbb{0}\right) = 0, \quad
\mu\left(\mathbb{1}\right) =  1, \quad
\mu\left(\proj{0}\right) = 1, \quad
\mu\left(\proj{1}\right) = 0, \quad
\mu\left(\proj{\ps}\right) = 1/2, \ldots
\end{array}\]
Note that, similarly to the classical case, the probability of
$\mathbb{1}$ is 1 and the probability of collections of orthogonal
events (e.g., $\proj{0}+\proj{1}$) is the sum of the individual
probabilities. In contrast, a collection of non-orthogonal events
(e.g., $\proj{0}$ and $\proj{\ps}$) is not itself an event.
In the classical example, we argued that each probability measure is
uniquely determined by two actual coins. A similar (but much more
subtle) argument is valid also in the quantum case. By postulates of
quantum mechanics and Gleason's theorem, it turns out that for large
enough quantum systems, each probability measure is uniquely
determined by an actual quantum state.
\end{example}

To properly explain the previous example and generalize to arbitrary
quantum systems, we formally define a quantum probability space as
follows.

\begin{definition}[Quantum Probability Space~\cite{BirkhoffVonNeumann1936,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu$ such that:\footnote {It is possible to define a more general
    space of events consisting of all operators~$\mathcal{A}$ on
    $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item The set of events contains the empty projection $\mathbb{0}$
  together with projection operators $\proj{\psi}$ for each state
  $\ket{\psi}$,
\item $\mu(\mathbb{1})=1$, and 
\item for projections expressible as sums $\sum_{i}E_{i}$ of
  necessarily orthogonal events $E_i$, we have
  $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$.
\end{itemize}
\end{definition}

\newpage
\amr{the rest needs cleaning up and perhaps does not even belong in
  this section}

Although it seems that we need an infinite
long table to specify the quantum probability measure~$\mu$, our $\mu$
is actually given by a simple formula~$\melement{0}{E}$. In general,
Born discovered each quantum state
$\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $ induces a probability
measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$ on the space of
events defined for any event $E\in\qevents$ as
follows~\cite{Born1984,Mermin2007}:
\begin{equation}
\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
The Born rule satisfies the following properties:
\begin{itemize}
\item It can be extend to mixed states. Given a mixed state represented
by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
the Born rule can be extended to $\rho$ by 
\begin{eqnarray}
\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}
Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
is a classical probability space. Therefore, when we discretize the
Hilbert space later, we may need to discretize this probability space
as well.\yutsung{Check!!!}
\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\yutsung{...I think I need to check these properties identify an
unique Born rule in CQT or something...}

@@

Although it seems that we need an infinite long table to specify the
quantum probability measure~$\mu$, our $\mu$ is actually
given by a simple formula~$\melement{0}{E}$. In general, Born discovered
each quantum state $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $
induces a probability measure $\tilde{\mu}_{\psi}:\qevents\rightarrow[0,1]$
on the space of events defined for any event $E\in\qevents$ as follows~\cite{Born1984,Mermin2007}:
\begin{equation}
\tilde{\mu}_{\psi}(E)=\frac{\melement{\psi}{E}}{\ip{\psi}{\psi}}\label{eq:Born}
\end{equation}
The Born rule satisfies the following properties:
\begin{itemize}
\item It can be extend to mixed states. Given a mixed state represented
by a density matrix $\rho=\sum_{j=1}^{N}q_{j}\frac{\proj{\psi_{j}}}{\ip{\psi_{j}}{\psi_{j}}}$,
where $\sum_{j=1}^{N}q_{j}=1$, i.e., $\Tr\left(\rho\right)=1$, then
the Born rule can be extended to $\rho$ by 
\begin{eqnarray}
\tilde{\mu}_{\rho}\left(E\right) & = & \Tr\left(\rho E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\Psi_{j}}\left(E\right)\textrm{ .}\label{BornRule.mixed}
\end{eqnarray}
Notice that $\left(\left\{ 1,\ldots,N\right\} ,2^{\left\{ 1,\ldots,N\right\} },\pmeas\left(J\right)=\sum_{j\in J}q_{j}\right)$
is a classical probability space. Therefore, when we discretize the
Hilbert space later, we may need to discretize this probability space
as well.\yutsung{Check!!!}
\item $\tilde{\mu}_{\rho}$ is a probability measure for all mixed state~$\rho$.
\item $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=0$.
\item $\tilde{\mu}_{\psi}\left(E\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}E\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\yutsung{...I think I need to check these properties identify an
unique Born rule in CQT or something...}

@@

\yutsung{There are three ways to characterize a quantum probability: 
\begin{enumerate}
\item The above two conditions as Gleason did. 
\item As a linear functional on a {*} algebra. 
\item As induced by a state vector by the Born rule (\ref{eq:Born}). 
\end{enumerate}
According to equation (37) in section 4 Quantum Probability in \cite{Maassen2010},
the equivalence between 1. and 2. only hold for $d\ge3$ because of
Gleason' theorem. Therefore, it seems hard to get insight for how
to handle Gleason's theorem by {*}-algebra formalism...

The equivalence between 2. and 3. can be found in Proposition 4.1.1
in \cite{Swart2013}. Here, the Born rule~$\mu_{\psi}(E)$ is replaced
by a faithful pseudotrace $\tau$ and $\mu_{\psi}(E)=\tau\left(\proj{\psi}E\right)$.
The faithful pseudotrace is defined in section 5.2 Decomposition of
algebra with a list of conditions. The problem is:
\begin{itemize}
\item Lemma 5.2.1 proved there exists a faith pseudotrace, but said nothing
about uniqueness. Therefore, these conditions may not uniquely determine
the Born rule?
\item We don't formulate thing in algebra... So although we may have an
analog or something, we cannot quite sure our conditions will be exactly
the same as theirs. 
\end{itemize}
If we admit the above, then the condition (a) to (c) and $\tau\left(AB\right)=\tau\left(BA\right)$
implies 
\begin{itemize}
\item Our map $\tilde{\mu}:\Hilb\rightarrow\qevents\rightarrow[0,1]$ should
satisfy $\tilde{\mu}_{\psi}$ is a probability measure for all $\ket{\psi}\in\Hilb\backslash\left\{ 0\right\} $.
\end{itemize}
The condition (a) and (d) implies
\begin{itemize}
\item Our map $\tilde{\mu}$ satisfy $\ip{\psi}{\phi}=0\Leftrightarrow\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{0}$,
where $\tilde{0}$ is $0$ for $\left[0,1\right]$ and $\tilde{0}$
is impossible for $\mathscr{L}_{2}=\left\{ \imposs,\poss\right\} $. 
\end{itemize}
$\tau\left(AB\right)=\tau\left(BA\right)$ also implies
\begin{itemize}
\item $\tilde{\mu}_{\psi}\left(\proj{\phi}\right)=\tilde{\mu}_{\mathbf{U}\ket{\psi}}\left(\mathbf{U}\proj{\phi}\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\ket{\psi},\ket{\phi}$ are states and $\mathbf{U}$ is any unitary
map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
Besides, the condition (a) also gives the probability of mixed states
form pure states... OK... it seems that I know what I am going to
type for DQT, but I think I need to sort them out before type them...}

@@

\amr{give example non-commuting events}
